---
title: "Assessment 2"
author: "Felita Pratomo S4660121"
date: '2022-03-18'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## *Felita Pratomo* **S4660121**

-----

# Assessment 2

----


###  Load the packages

```{r}
library(tidyverse)

library(knitr)

library(skimr)

library(readr)
```



### Load the dataset
```{r}

thanksgiving_meals <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-20/thanksgiving_meals.csv")  

```



### 1. Display the first 10 rows of the dataset using `kable()` function (1 marks). 

```{r}

kable(thanksgiving_meals[1:10, 1:5])

```



### 2. Using `skim()` display the summary of variables. 

Think about the task to predict a family income based on their menu: what variables may be useful? Are all of them correct type? 
  Write 2-3 sentences with your explanation. (2 marks)

Think about the task to predict a community type or US_region based on their menu: what variables may be useful? Are all of them correct type? (2 marks)


```{r}

skim(thanksgiving_meals)

```

Variables that might be useful to predict a family income based on their menu are the main dish and cranberry sauce.
Logically, we might be able to see which family can afford more expensive main dish and either cranberry sauce is homemade or bought. 
Also, judging by their unique values, main dish has 8 and cranberry sauce has 4 which might boost the prediction accuracy rate. 


Variables that might be useful to predict a community type or US region based on their menu are cranberry sauce, sides, pies. 
We might be able to tell whether a certain region/community type has a culture of making their own cranberry sauce, choosing certain sides or any favorite pies. 
Otherwise, their unique values might be able to help predict the family income. 



### 3. Use `fct_reorder` and `parse_number` functions to create a factor variable `family_income`(2 mark).

```{r}

thanksgiving_meals <- thanksgiving_meals %>%
  mutate(family_income = fct_reorder(family_income, parse_number(family_income)))

class(thanksgiving_meals$family_income)

```



### 4. What is the number of people who celebrate? (1 mark)

The number of people who celebrate is 980.

```{r}
thanksgiving_meals %>%
  count(celebrate, sort = TRUE) %>%
  rename("No. of people" = n) %>%
  kable()
```



### 5. What are categories and insights for each main dish served and the method it is prepared? (2 marks)


```{r}
thanksgiving_meals %>%
  summarise(main_dish, main_prep) %>%
  count(main_dish, main_prep, sort = TRUE) %>%
  rename("Main Dish" = main_dish, "Cooking Method" = main_prep, "No. of Households" = n) %>%
  kable()
```

From the table above, we can gain some insights as follows:

- The most popular main dish for thanksgiving is Turkey with two methods: "baked" by 422 households and "roasted" by 351 households. 

- The second most popular main dish is Ham/Pork with two methods: "baked" by 22 households and "roasted" by 5 households.

etc. 



### 6. Create 3 different data viz showing insights for main dish served and the method. Provide your own legend and use themes.
Write 2-3 sentences with your explanation of each insight. (4 marks)


```{r}
thanksgiving_meals %>%
  count(main_prep, main_dish) %>%
  ggplot(aes(main_dish, n, fill = main_prep)) +
  geom_col() +
  facet_wrap(~main_prep) +
  coord_flip() +
  theme_minimal() +
  labs(title = "Number of Main Dish by Cooking Methods", fill = "Cooking Methods", x = "Main Dish", y = "Number of Main Dish", caption = "Data Viz 1: Bar Graph")
 
```

Data Viz 1 above shows "Turkey" as the most popular main dish with "Baked" as the most popular cooking method.



```{r}
thanksgiving_meals %>%
  count(main_dish, main_prep, community_type) %>%
  ggplot(aes(main_dish, n, fill = main_prep)) +
  geom_col(col = "black") +
  scale_fill_brewer(palette = "Spectral") +
  facet_wrap(~community_type) +
  coord_flip() +
  theme_grey() +
  labs(title = "The distribution of Main Dish by its Cooking Methods in different Community Types", 
       fill = "Cooking Method", x = "Main Dish", y = "No. of Households", caption = "Data Viz 2: Bar Graph") 
```

Data Viz 2 above shows that the most popular cooking methods in different community types are "Roasted" and "Baked" with similar percentage in distribution between the two methods. 



```{r}
thanksgiving_meals %>%
  count(main_dish, main_prep, gender) %>%
  ggplot(aes(main_dish, n, fill = main_prep)) +
  geom_col() +
  facet_wrap(~gender) +
  coord_flip() +
  theme_bw() +
  labs(title = "The distribution of Main Dish by its Cooking Methods in different Gender", 
       fill = "Cooking Method", x = "Main Dish", y = "No. of Households", caption = "Data Viz 3: Bar Graph") 
```

Data Viz 3 above shows the distribution of Main Dish by its Cooking Methods in different Gender.
It can be seen that there is no huge difference in the distribution between Female and male. 
The most popular cooking methods are still "Roasted" and "Baked". 



### 7. How many use cranberry sauce? How many use gravy? 2marks

```{r}

thanksgiving_meals %>%
  count(cranberry, sort = TRUE) %>%
  rename("No. of people" = n) %>%
  kable()
  
thanksgiving_meals %>%
  count(gravy, sort = TRUE) %>%
  rename("No. of people" = n) %>%
  kable()
  
```

According to the data, there are 828 people who use cranberry sauce and 892 people who use gravy. 



### 8-9. What is the distribution of those who celebrate across income ranges. Create a data viz.
Write 2-3 sentences with your explanation of each insight. (4 marks)


The graph below explains the distribution of households who celebrate thanksgiving across their income ranges. 
It can be seen that thanksgivings are most celebrated by households who have a total income range of $25,000 to $49,999.
Households who celebrate that have more than a total income range of $125,000 above are much lesser in number compared to the lower income ranges. 


```{r}

thanksgiving_meals %>%
  count(family_income, celebrate) %>%
  filter(celebrate == "Yes") %>%
  ggplot(aes(family_income, n)) +
  geom_col() +
  facet_grid(~celebrate) +
  coord_flip() +
  labs(title = "The Distribution of Households Who Celebrate across Their Income Ranges", x = "Family Income", y = "No. of People")

```



### 10. Use the following code to create a new data set 2 mark


```{r}

thanksgiving_2 <- thanksgiving_meals %>% 
  select(id, starts_with("side"),
       starts_with("pie"),
       starts_with("dessert")) %>%
  select(-side15, -pie13, -dessert12) %>%
  gather(type, value, -id) %>%
  filter(!is.na(value),
         !value %in% c("None", "Other (please specify)")) %>%
  mutate(type = str_remove(type, "\\d+"))

```

#### Write 2-3 sentences with your explanation of what it does. (4 marks)

The code above is to sort what people have for their sides, pies and desserts in a new dataset, 
with an exception to exclude side 15, pie 13 and dessert 12. Then, gathered it by three columns 
type, value and id (which already existed) with conditions to remove NA value by using filter function, also none and other values. 




### 11-12. Intall package `widyr` and use `pairwise_cor()` function https://www.rdocumentation.org/packages/widyr/versions/0.1.3/topics/pairwise_cor 
#### Write 2-3 sentences with your explanation of what it does. (2 marks)

The function "pairwise_cor()" shows correlations of pairs of items in a column, based on a "feature" column that links them together.


#### Write 1 sentence with your explanation of what insights it shows. (2 marks)

The code below sorts the outcome by descending order and the result shows cookies and brownies have the top correlation number of 0.410.

```{r}
#install.packages("widyr")

library(widyr)


thanksgiving_2 %>%
  pairwise_cor(value, id, sort = TRUE) 
```




### 13. Use `lm()` or randomForest() function to build a model that predict a family income based on data in the dataset. 8 marks
### Compare 3 models using different set of input variables. Use different number of variables.

#### Explain your choice of variables (3 sentences) 


```{r}
#install.packages("randomForest")

library(randomForest)

```


First Model: using 3 variables (main dish, cranberry sauce and gender).

```{r}
rf1 <- randomForest(family_income ~ main_dish + cranberry + gender, data = thanksgiving_meals, na.action = na.omit)

print(rf1)
```


Second Model: using 5 variables (main dish, cranberry sauce, community type, gender, and age).

```{r}
rf2 <- randomForest(family_income ~ main_dish + cranberry + community_type + gender + age, data = thanksgiving_meals, na.action = na.omit)

print(rf2)
```


Third Model: using 7 variables (main dish, main prep, cranberry, age, gender, us region, and work black friday).

```{r}
rf3 <- randomForest(family_income ~ main_dish + main_prep + cranberry + age  + gender + us_region + work_black_friday, data = thanksgiving_meals, na.action = na.omit)

print(rf3)
```


#### Write 2 sentences explaining which model os best.

From the results, it can be seen that Model 2 is probably the best out of the 3 models tested above as it generates the lowest error rate. 







